### 2025-06-10 index.qmd
20250609 - typo
20250610 - acknowledgment

The GitHub repository for the book is located here:\index{GitHub} <https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook>.
If you have data or analysis examples that are you are willing to share and include in the book, feel free to contact me.

@@

I thank Dr. Benjamin Motz, who provided consultation and many helpful resources based on his fantasy football statistics class.
I also thank key members of [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), including Val Pinskiy, Andrew Tungate, Dennis Andersen, and Adam Peterson, who helped develop and provide fantasy football-related resources and who helped sharpen my thinking about the topic.
I also thank Professor Patrick Carroll, who taught me the value of statistics for answering important questions.

>>>>

The GitHub repository for the book is located here:\index{GitHub} <https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook>.
If you have data or analysis examples that you are willing to share and include in the book, feel free to contact me.

@@

I thank Dr. Benjamin Motz, who provided consultation and many helpful resources based on his fantasy football statistics class.
I also thank key members of [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), including Val Pinskiy, Andrew Tungate, Dennis Andersen, and Adam Peterson, who helped develop and provide fantasy football-related resources and who helped sharpen my thinking about the topic.
In particular, Andrew Tungate made important additions to the [`ffanalytics` `R` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics] that were necessary for conducting a [bootstrap simulation](#sec-simulationProjectedPointsBootstrapping) of players' projected fantasy points.
I also thank Professor Patrick Carroll, who taught me the value of statistics for answering important questions.
